# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
Loading required libraries
```{r, echo = TRUE}
install.packages("ggplot2")
library(ggplot2)
```
Downloading data
```{r, echo = TRUE}
setwd("d:/DEV/R/Learning")
#fileUrl="https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
fileURL="https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
if(!file.exists("gettingData")){
  dir.create("gettingData")
}
setwd("d:/DEV/R/Learning/gettingData")
download.file(fileUrl, destfile = "activity.zip", method="auto")
list.files(".//gettingData")
activityDateDownloaded = date()
```

Loading activities data and changing  the date into a format suitable for our analysis:
```{r preparation, echo = TRUE}
activities=read.csv(unz(description ="activity.zip", "activity.csv"), sep=",")
str(activities)
activities$date = as.Date(activities$date, format="%Y-%m-%d")
activities$fdate = factor(activities$date)
activities$finterval = factor(activities$interval)
```



## What is mean total number of steps taken per day?
```{r, echo = TRUE}
sumData=tapply(activities$steps, activities$fdate,sum, na.rm=TRUE)
png(filename=".//figure/Total_number_of_steps_per_day_(Histogram).png", width = 480, height = 480, units = "px", pointsize = 12, bg = "white", res = NA, family = "", restoreConsole = TRUE)
hist(sumData)
dev.off()

mean(sumData, na.rm = TRUE)
median(sumData, na.rm = TRUE)
```


## What is the average daily activity pattern?
```{r, echo = TRUE}
library(ggplot2)
#avgData=tapply(activities$steps, factor(activities$interval),mean, na.rm=TRUE)
avgData=tapply(activities$steps, activities$interval,mean, na.rm=TRUE)
avg = data.frame(dimnames(avgData),avgData)
names(avg)=c("Interval", "Activities")
#png(filename=".//figure/Average_Daily_Activity_Pattern.png", width = 480, height = 480, units = "px", pointsize = 12, bg = "white", res = NA, family = "", restoreConsole = TRUE)
#ggplot2(activities$fdate, sumData, type="l")

#qplot(avg$Interval, avg$Activities, geom = "path")
plot(avg$Interval, avg$Activities, type = "l")
ggplot() +
geom_point(data = avg, aes(x = Interval, y = Activities),colour = 'red', size = 1) 
  #geom_point(data = ds, aes(x = gp, y = mean),
  #                      colour = 'red', size = 3) +
  #geom_errorbar(data = ds, aes(x = gp, y = mean,
   #                 ymin = mean - sd, ymax = mean + sd),
    #                colour = 'red', width = 0.4)
#dev.off()
#intervalOfMaxAverageStepsNo = max(avg$)
```


## Imputing missing values
```{r, echo = TRUE}

```


## Are there differences in activity patterns between weekdays and weekends?
```{r, echo = TRUE}

```