# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
Loading required libraries
```{r, echo = TRUE}
library(ggplot2)
```
Downloading data
```{r, echo = TRUE}
setwd("d:/DEV/R/Learning")
#fileUrl="https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
fileURL="https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
if(!file.exists("gettingData")){
  dir.create("gettingData")
}
setwd("d:/DEV/R/Learning/gettingData")
download.file(fileUrl, destfile = "activity.zip", method="auto")
list.files(".//gettingData")
activityDateDownloaded = date()
```

Loading activities data and changing  the date into a format suitable for our analysis:
```{r preparation, echo = TRUE}
activities=read.csv(unz(description ="activity.zip", "activity.csv"), sep=",")
str(activities)
activities$date = as.Date(activities$date, format="%Y-%m-%d")
activities$fdate = factor(activities$date)
```



## What is mean total number of steps taken per day?
```{r, echo = TRUE}
sumData=tapply(activities$steps, activities$fdate,sum, na.rm=TRUE)
hist(sumData)
mean(sumData, na.rm = TRUE)
median(sumData, na.rm = TRUE)
```


## What is the average daily activity pattern?
```{r, echo = TRUE}
library(ggplot2)
plot(activities$fdate, sumData, type="l")
```


## Imputing missing values
```{r, echo = TRUE}

```


## Are there differences in activity patterns between weekdays and weekends?
```{r, echo = TRUE}

```