---
output: html_document
---
# Reproducible Research: Peer Assessment 1
This report is on activities of a person that is captured via a device for two month every 5 minutes. This report will explore these data and perform some basic data analysis on them.

## Loading and preprocessing the data
### Loading required libraries
```{r Libraries, echo = TRUE}
#install.packages("ggplot2")
library(ggplot2)
```
### Downloading data
Data are downloaded from http://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip. The link is to a zip file that contains a single csv file namely, activity.csv. The file is assumed to be downloaded and extratced to the working directory of this application prior to generating the report.

```{r Downloads, echo = TRUE}
setwd("D:/Woking/AHA/DEV/John Hopkins Data Science/ReproducibleResearch/RepData_PeerAssessment1")

#fileURL="http://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
#if(!file.exists("gettingData")){
  #dir.create("gettingData")
#}

#download.file(fileURL, destfile = "activity.zip", method="auto")
#list.files(".//gettingData")
#activityDateDownloaded = date()
```

Loading activities data and changing  the date into a format suitable for our analysis:
```{r Data Preparation, echo = TRUE}
activities=read.csv(unz(description ="activity.zip", "activity.csv"), sep=",")
str(activities)
activities$date = as.Date(activities$date, format="%Y-%m-%d")
activities$fdate = factor(activities$date)
activities$finterval = factor(activities$interval)
```



## What is mean total number of steps taken per day?
```{r Graph of mean of the total number of steps taken per day, echo = TRUE}
sumData=tapply(activities$steps, activities$fdate,sum, na.rm=TRUE)
png(filename=".//figure/Total_number_of_steps_per_day_(Histogram).png", width = 480, height = 480, units = "px", pointsize = 12, bg = "white", res = NA, family = "", restoreConsole = TRUE)
sum = data.frame(dimnames(sumData),sumData)
names(sum)=c("Date", "Steps")
hist(sumData)

dev.off()
png(filename=".//figure/Total_number_of_steps_per_day.png", width = 480, height = 480, units = "px", pointsize = 12, bg = "white", res = NA, family = "", restoreConsole = TRUE)
a = ggplot(data = sum, aes(x=as.Date(Date), y=Steps), ordered=TRUE) + geom_line() + geom_point()+
  labs(x = "Month", y = " Total Number of Steps Taken Each Day")
a

dev.off()
```

The mean and median
```{r Mean of the total number of steps}
oldMean = mean(sumData, na.rm = TRUE)
oldMedian = median(sumData, na.rm = TRUE)
```


## What is the average daily activity pattern?
```{r Average daily activity pattern, echo = TRUE}


avgData=tapply(activities$steps, activities$interval,mean, na.rm=TRUE)
avg = data.frame(dimnames(avgData),avgData)
names(avg)=c("Interval", "Activities")
png(filename=".//figure/Average_Daily_Activity_Pattern.png", width = 480, height = 480, units = "px", pointsize = 12, bg = "white", res = NA, family = "", restoreConsole = TRUE)

ggplot(data= avg, aes(x = order(Interval), y = Activities), ordered=TRUE) + geom_line() + geom_point(colour = 'red', size = 3)+
  xlab("Interval") +
  ylab("Average number of steps taken, averaged across all days") +
  ggtitle("Average Daily Activity Pattern")
  
dev.off()
intervalOfMaxAverageStepsNo_Index = which.max(avg$Activities)
intervalOfMaxAverageStepsNo_Value = max(avg$Activities)
```


## Imputing missing values
###The total number of missing values in the dataset:
```{r number of missing values, echo = TRUE}
missingActivities = activities[is.na(activities$steps),]
missingActivitiesNO=length(missingActivities$steps)
activitiesNO =  length(activities$steps)
```

###Filling of missing values in the dataset:
```{r Filling missing values, echo = TRUE}

names(avg)=c("interval", "averageStepsByInterval")
averagedActivitiesByIntertval=merge(activities, avg, by.x="interval",by.y="interval")
missingActivitiesIndices = which(is.na(averagedActivitiesByIntertval$steps))
averagedActivitiesByIntertval[missingActivitiesIndices,2] = averagedActivitiesByIntertval[missingActivitiesIndices,6]
correctedActivities = averagedActivitiesByIntertval[,1:5]
```

###Graph of the corrected activities of the total number of steps taken each day
```{r Graph of mean of the total number of steps taken per day after imputing missing data, echo = TRUE}
correctedSumData=tapply(correctedActivities$steps, correctedActivities$fdate,sum, na.rm=TRUE)
png(filename=".//figure/Total_number_of_steps_per_day_(Histogram)(corrected).png", width = 480, height = 480, units = "px", pointsize = 12, bg = "white", res = NA, family = "", restoreConsole = TRUE)
correctedSum = data.frame(dimnames(correctedSumData),correctedSumData)
names(correctedSum)=c("Date", "Steps")
hist(correctedSumData)

dev.off()
png(filename=".//figure/Total_number_of_steps_per_day_(corrected).png", width = 480, height = 480, units = "px", pointsize = 12, bg = "white", res = NA, family = "", restoreConsole = TRUE)
a = ggplot(data = correctedSum, aes(x=as.Date(Date), y=Steps), ordered=TRUE) + geom_line() + geom_point()+
  labs(x = "Month", y = " Total Number of Steps Taken Each Day")
a

dev.off()
```

###The mean and median of the corrected activities
```{r New mean of the total number of steps}
newMean = mean(correctedSumData, na.rm = TRUE)
newMedian = median(correctedSumData, na.rm = TRUE)
```
####Do these values differ from the estimates from the first part of the assignment? 
Yes they differ the mean and median have increased slightly
##### Old values
```{r old mean and median}
oldMean
oldMedian
```
##### New Values
```{r}
newMean
newMedian
```
####What is the impact of imputing missing data on the estimates of the total daily number of steps?
The distribution of the data has changed a little. There is an increase in the frequency of the number of steps in general. The maxima of the number of steps is has remained the same while the minima have definitely increased. the mean and median have increased slightly.
## Are there differences in activity patterns between weekdays and weekends?
```{r differences in activity, echo = TRUE}

```